Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-13 analysis/paper/paper.Rmd
Add section and references on related discipline efforts

>>>>

## Efforts and Examples from Related Disciplines

Plant pathology is not alone in the lack of reproducibility and with the close-nature of data and code.
In response to this, other related disciplines have published guides or started communities to promote and support tools and methods that promote good practices that lead to open and reproducible research.In entomology @Wittman2020 published "A Guide and Toolbox to Replicability and Open Science in Entomology", which documented both the benefits and drawbacks of an open and reproducible workflow.
Weed scientists started a community to promote openness in the discipline, Open Weed Science, which stated that they valued, "open access knowledge-sharing as a strategy to enhance reproducibility within our discipline", but the website is no longer available and the Twitter account, \@OpenWeedSci, appears to be inactive when viewing the account as of October 2022 [@OpenWeedScience2021].
@SerradaCruz2019 proposed a framework for capturing provenance of data-centric agronomic experiments using an R-based workflow, 'RFlow', which would allow reuse of R scripts using generic workflows and saving data and metadata to web repositories that other researchers and referees can browse using Web interfaces.
@Kool2020 evaluated the reproducibility of on-farm experiments in Africa, finding that often the experimental design was difficult or impossible to reproduce from the publication.
More broadly within agricultural research, articles have been published highlighting the advantages of, need for and how to publish FAIR data in agriculture, [@Smith2018; @Arnaud2020; @Stacey2022].
However, we were unable to find any quantification of the reproducibility of any of these related disciplines as we have done here.
